---
title: "Identifying store chains"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
```

```{r load packages,message=FALSE,warning=FALSE}
library(tidyverse)
library(sf)
```

## Loading data
We start by loading tracts, particularly a dummy variable that shows whether a tract is in the Atlanta urbanized area.

```{r tract load}
tracts_ua<-st_read("Data/Tract_UA_Atlanta_individual.shp", quiet=TRUE)[,c(1,2,4)] %>%
  mutate(GISJN_TCT=paste("G",tractid,sep=""))
st_geometry(tracts_ua)<-NULL
```

Then we also load our store data and join the tract data

```{r store load,message=FALSE}
storedata<-read_csv("Data/GA_SNAPstores_2008_2016_GeoID_dummy.csv") %>%
  right_join(tracts_ua) 
```

##Working with the data

We convert the store data to long format and just select stores present in each year.

```{r filter data}
storedata_long<-storedata %>%
  gather(Y2008:Y2016,key="year",value="st_value") %>%
  gather(walmart:big.lots,key="store",value="value") %>%
  filter(value==1,st_value==1) %>%
  select(-value,-st_value)
```
```{r, echo=FALSE}
storedata_long %>% head() %>% kable()
```

Some SNAP retailers are classified in different ways across years. We identify chain type by the most common classification as shown below.

```{r store class}
storedata_type<-storedata_long %>%
  group_by(store,STTYPE) %>%
  summarise(count=n()) %>%
  ungroup()%>%
  group_by(store) %>%
  filter(count==max(count)) %>%
  select(-count)
```
```{r, echo=FALSE}
storedata_type %>% head() %>% kable()
```

Lastly, we create a count of stores in each year and look at the minimum values. We select just those store with a minimum of 20 or more.

```{r}
atl_stcount<-storedata_long %>%
  group_by(store,year) %>%
  summarise(count=n()) %>%
  ungroup() %>%
  group_by(store) %>%
  summarise(min=min(count)) %>%
  filter(min>19) %>%
  left_join(storedata_type) %>%
  arrange(STTYPE,desc(min))
```
```{r, echo=FALSE}
atl_stcount %>% kable()
```